Using temperature distributions of active regions to investigate flare activity

### 2014-12-11 paper.tex
Updates to analysis code
Structure changed slightly to fit guidelines
Plotting of temperature change over time added

@@

\subsection{Active region analysis}
The method of Paper I was used to investigate the temperatures of flaring active regions betwen AR11138-AR11183. %substitute dates here
The first part of the investigation tracked active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
Then the temperatures of the associated active regions were directly compared for each of the investigated flares.

@@

%===========================================================================
\section{Results}
Figures 1 and 2 show the mean, standard deviation, 95th percentile and maximum temperature of active regions AR11146 and AR11149 respectively, as functions of time.
The times of the associated flares are also plotted. These regions were chosen as they are typical of the results found for other active regions, and show similar temperature profiles but different numbers of flares. In both plots, some time before a flare or group of flares occur, the maximum temperature rises significantly but the bulk temperature of the region varies relatively little.
Figure 3 plots the peak flux for all flares associated with the studied active regions against the 95th percentile temperature for the corresponding active regions before the beginning of the flare.
Most of these flares are grouped around log(T) $\approx$ 6.35, 6.55 and 6.7, with fewer flares associated with hotter active regions, generally.
However, the strongest flares observed do appear to be associated with hotter active regions.

%===========================================================================
\section{Discussion}

@@

%===========================================================================
\section{Conclusions}

>>>>

%===========================================================================
\begin{abstract}
  This is an abstract
\end{abstract}

@@

\subsection{Active region analysis}
The method of Paper I was used to investigate the temperatures of the active regions associated with flares which occured betwen 2011-02-01 and 2011-04-01.
% Currently the dates are 2011/02/10 - 2011/02/16, which needs some fixing
The first part of the investigation tracked active regions as they moved across the solar disk and plotted their temperature distributions in the hour leading up to a flare.
Then the temperatures of the associated active regions were directly compared for each of the investigated flares.

@@

%===========================================================================
\section{Results}
%Figures 1 and 2 show the mean, standard deviation, 95th percentile and maximum temperature of active regions AR11146 and AR11149 respectively, as functions of time. %None of this is true6 becaus6e I'm not doing those plots any more
The times of the associated flares are also plotted.
These regions were chosen as they are typical of the results found for other active regions, and show similar temperature profiles but different numbers of flares.
In both plots, some time before a flare or group of flares occur, the maximum temperature rises significantly but the bulk temperature of the region varies relatively little.
Figure 3 plots the peak flux for all flares associated with the studied active regions against the 95th percentile temperature for the corresponding active regions before the beginning of the flare.
Most of these flares are grouped around log(T) $\approx$ 6.35, 6.55 and 6.7, with fewer flares associated with hotter active regions, generally.
However, the strongest flares observed do appear to be associated with hotter active regions.

%===========================================================================
\section{Discussion and conclusions}

@@

%===========================================================================
\section*{Acknowledgements}

%===========================================================================
\section*{annexes}
